### 2020-04-26 thesis_template/1_Intro/intro.tex
document updated

\section{Motivation}
\label{sec:motivation}
Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies have democratized data driven businesses by 
eliminating significant amount of initial investment.

>>>>

\section{Motivation}
\label{sec:motivation}
Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies has democratized data driven businesses by 
eliminating significant amount of initial investment.

### 2020-04-26 thesis_template/2_RelatedWork/model/linalg.tex
document updated

\section{BLAS LAPACK}
\label{sec:history}

@@

\section{Netlib-Java}
\label{sec:history}

@@

\section{Create Java interface of CBLAS with JNI}
\label{sec:history}
\begin{enumerate}
    \item Download BLAS and build using make file. In the figure2.1, the built file is libblas.a and the header file is blas.h.
    \item Download CBLAS and build using make file (I am not sure whether we should build archive file or shared library). In figure, the build file would be libcblas.a or libcblas.dylib and header file is cblas.h.
    \item Create java file which will be the Java interface of CBLAS.
    \item Compile java file with -h header flag to create class file (CBLASJ.class) and header file (CBLASJ.h).
\begin{lstlisting}[language=bash]
    $ javac -h . CBLASJ.java
\end{lstlisting}
    \item Create C file (CBLASJ.c) which will bind Java interface and CBLAS library. And compile it with JNI to create object file (CBLASJ.o).
\begin{lstlisting}[language=bash]
    $ gcc -c-fPIC -I${JAVA_HOME}/include -I${JAVA_HOME}/include/darwin CBLASJ.c
\end{lstlisting}
    \item Compile shared library linking library (libcblas.a or libcblas.dylib) object file (CBLASJ.o).
\begin{lstlisting}[language=bash]
    $ gcc -o libcblas.dylib (or libcblas.a) CBLASJ.o 
\end{lstlisting}
\end{enumerate}

\begin{figure}[htb]
    \includegraphics[width=15cm]{cblas_with_jni.eps}
    \caption{Integration of Native Methods }
    \label{fig:Sampling}
\end{figure}

\section{Matrix Computation and Optimization in Apache Spark}
\label{sec:history}

@@

\section{Memory Management of each Linear Algebra Library}
\label{sec:history}

>>>>

\subsection{BLAS LAPACK}
\label{sec:linalg_blas_lapack}

@@

\subsection{Netlib-Java}
\label{sec:linalg_netlib}

@@

\subsection{Matrix Computation and Optimization in Apache Spark}
\label{sec:linalg_spark_marix}

@@

\subsection{Memory Management of each Linear Algebra Library}
\label{sec:linalg_memmanage}

### 2020-04-26 thesis_template/2_RelatedWork/model/os.tex
document updated

\section{Memory and Process in Operating Systems}
\label{sec:history}
A process is a section of computation job. A process can work on a CPU core. We can divide process as well.
Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create other child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

@@

\section{Multi-threading and Parallelism}
\label{sec:history}
A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
communicate each other, such as sharing memory and message passing.

\section{Memory management in Operating System}
\label{sec:history}
In computer storage hierarchy, the closest storage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
However, the same cannot be said of main memory, which is accessed via a transaction on the memory bus. This takes many cycles of the CPU clock.
The remedy is to add fast memory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.

@@

\section{Demand Paging}
\label{sec:history}
A process can have multiple pages. However, loading entire executable code from secondary storage to memory is not necessarily needed to 
get jobs done. A strategy used in several operating systems is loading only the portion of programs that are needed, demand page.

@@

\section{Copy on Page}
\label{sec:history}
When a parent process creates child process and if these process shares contents on particular page and modify it, 
only the page which has the context will be copied.

% \section{Threads and Concurrency}
% \label{sec:history}

>>>>

\subsection{Memory and Process in Operating Systems}
\label{sec:os_mem_process}
A process is a subsection of computation job. A process can work on a CPU core. We can divide process as well.
Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create other child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

@@

\subsection{Multi-threading and Parallelism}
\label{sec:os_thread}
A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
communicate each other, such as sharing memory and message passing.

\subsection{Memory management in Operating System}
\label{sec:os_memmanage}
In computer storage hierarchy, the closest storage to CPU is register. It is built into each CPU core and accessible within one cycle of the CPU clock.
However, the same cannot be said of main memory, which is accessed via a transaction on the memory bus. This takes many cycles of the CPU clock.
The remedy is to add fast memory between the CPU and main memory, typically on the CPU chip for faster access. Such a cache plays a role for this.

@@

\subsection{Demand Paging}
\label{sec:os_paging}
A process can have multiple pages. However, loading entire executable code from secondary storage to memory is not necessarily needed to 
get jobs done. A strategy used in several operating systems is loading only the portion of programs that are needed, demand page.

@@

\subsection{Copy on Page}
\label{sec:os_copypage}
When a parent process creates child process and if these process shares contents on particular page and modify it, 
only the page which has the context will be copied.

% \subsection{Threads and Concurrency}
% \label{sec:history}

### 2020-04-26 thesis_template/3_Body/chapter/concept.tex
document updated

\subsection{Type of Variable}
\label{sec:concept_diffval}
In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
However, one can select any variable types for operation in most case.

@@

\subsection{Reference Count}
\label{sec:concept_refcount}
Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.

@@

\subsection{Multithread}
\label{sec:concenpt_multithreading}
In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
One can implement various concurrent codes for the same purpose with different memory management strategies. 
The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).

@@

\subsection{Tree-aggregate}
\label{sec:concept_treeagg}
Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.

@@

\subsection{K-Nearest-Neighbors}
\label{sec:concept_history}
The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
Then, it checks corresponding categories of the \(K\) observations to determine predicted category.

@@

\subsection{Complex Objects}
\label{sec:concept_history}
To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
CustomerRc acquires Rc of values used for its fields from the source Vec.

@@

 \subsection{Wikipedia Data Sets}
 \label{sec:concept_dataset}
 Wikipedia page data sets are used to perform document classification with KNN. 
 \(10^5\) pages are used for training data set, and 18724 pages are used for target.

 \subsection{Experimental Details}
 \label{sec:concept_expdetail}
 Our experiments are run on three types of VM instances on Google Cloud Platform: 
 n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
 All of the experiments described are performed 5 times. 
 In this thesis, we present the average of 5 separate runs for each experiment.
\clearpage

>>>>

\section{Type of Variable}
\label{sec:concept_diffval}
In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
However, one can select any variable types for operation in most case.

@@

\section{Reference Count}
\label{sec:concept_refcount}
Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.

@@

\section{Multithread}
\label{sec:concenpt_multithreading}
In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
One can implement various concurrent codes for the same purpose with different memory management strategies. 
The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).

@@

\section{Tree-aggregate}
\label{sec:concept_treeagg}
Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.

@@

\section{K-Nearest-Neighbors}
\label{sec:concept_history}
The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
Then, it checks corresponding categories of the \(K\) observations to determine predicted category.

@@

\section{Complex Objects}
\label{sec:concept_history}
To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
CustomerRc acquires Rc of values used for its fields from the source Vec.

@@

\clearpage

### 2020-04-26 thesis_template/3_Body/chapter/evaluation.tex
documented llvm
labled documentation
document updated

\subsection{Experiment for Accessing Object with Different Variable Type}
\label{sec:history}
\input{3_Body/model/access_own_reference_slice}
\clearpage

\subsection{Assessment of different reference methods in Rust}
\label{sec:history}
\input{3_Body/model/drop_ref_rc}
\clearpage

\subsection{Experiment for Merge-sort}
\label{sec:history}
\input{3_Body/model/merge_sort_experiment}
\clearpage

\subsection{Experiment for Tree-aggregation}
\label{sec:history}
\input{3_Body/model/tree_aggregate_experiment}
\clearpage

\subsection{Elements Copy and Insertion into Size-initialized Vector in Rust.}
\label{sec:history}
\input{3_Body/model/element_copy_initialization}

>>>>

\section{Experimental Set and Detail}
\label{sec:eval_setdetail}
\input{3_Body/model/experimental_set_detail}
\clearpage

\section{Experiment 1: Accessing Object with Different Variable Type}
\label{sec:eval_diffval}
\input{3_Body/model/access_own_reference_slice}
\clearpage

\section{Experiment 2: Assessment of different reference methods in Rust}
\label{sec:eval_refcount}
\input{3_Body/model/drop_ref_rc}
\clearpage

\section{Experiment 2: Merge-sort}
\label{sec:eval_sort}
\input{3_Body/model/merge_sort_experiment}
\clearpage

\section{Experiment 4: Tree-aggregation}
\label{sec:eval_treeagg}
\input{3_Body/model/tree_aggregate_experiment}
\clearpage

% \section{Elements Copy and Insertion into Size-initialized Vector in Rust.}
% \label{sec:history}
% \input{3_Body/model/element_copy_initialization}
